\LARGE \bf Steering a Swarm Using Global Inputs\\ and Swarm Statistics

### 2017-10-03 journalSwarmControl/experiment.tex
New plots have been added
Added the plots

%\subsection{Automated object manipulation (simulation)}
Fig.~\ref{fig:story} shows snapshots during an execution of this algorithm in simulation. 
Experimental results of parameters sweeps are summarized in Fig.~\ref{fig:AutoVeryParam}.  Each trial measured the time to deliver the object to the goal location.  The default parameter settings used 100 robots, a normalized weight of 1, a hexagon shape, and Brownian noise (applied once each simulation step) with $W=5$.

@@

>>>>

%\subsection{Automated object manipulation (simulation)}
Fig.~\ref{fig:story} shows snapshots during an execution of this algorithm in simulation.
 We also have tested two other mazes with ``E'' shape and a ``Spiral'' without changing the algorithm to illustrate the capability of the algorithm in Fig.~\ref{fig:Emaze}. Fig.~\ref{fig:DifferentMazes} shows the results of all the three different mazes. E-shape maze has the least average time because the path to the goal is shorter. 
 Experimental results of parameters sweeps are summarized in Fig.~\ref{fig:AutoVeryParam}.  Each trial measured the time to deliver the object to the goal location.  The default parameter settings used 100 robots, a normalized weight of 1, a hexagon shape, and Brownian noise (applied once each simulation step) with $W=5$.

@@

\begin{figure}
\centering
\begin{overpic}[width=0.4\columnwidth]{MDPEmaze.pdf}\end{overpic}
\begin{overpic}[width=0.4\columnwidth]{EmazeFinal.pdf}\end{overpic}\\
\vspace{0.5em}
\begin{overpic}[width=0.4\columnwidth]{Spiral.pdf}\end{overpic}
\begin{overpic}[width=0.4\columnwidth]{SpiralSuccess.pdf}\end{overpic}
\caption{\label{fig:Emaze} We have tested multiple mazes to illustrate that the algorithm works for different environments.
}
\end{figure}
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{DifferentShapes.pdf}\end{overpic}
\vspace{-2em}
\caption{\label{fig:DifferentMazes} Different maps and mazes were tested to validate the algorithm. E-shape maze has the least completion time average because it has the shortest path to the goal from the starting position.
}
\end{figure}
